---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wnbaherstory

<!-- badges: start -->
<!-- badges: end -->

## Overview

The goal of wnbaherstory is to provide historical data on the WNBA. Users can discover past and present WNBA teams, player history, player awards, game attendance and more. 

## Installation

You can install the development version of wnbaherstory from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("sds270-f24/wnbaherstory")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wnbaherstory)
## basic example code
```

## Contributors
 - [Jane Loo](https://github.com/janeloo10)
 - [Ella Sylvester](https://github.com/esylvester04)
 - [Alina Abdulina](https://github.com/AlinaAbdulina)
